Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-03 paper/ms.tex
Minor change
Update numbers in text

First, we illustrate the time-dependence of one possible inaccurate reference
frame. We begin by taking an orbit with initial position $(8, 0, 0)\,\kpc$ and
initial velocity $(0, -190, 50)\,\kms$ --- this corresponds to an orbit with
actions $(J_r, L_z, J_z) = (32.5, -1520, 23.0)\,\actunit$ and
$z_{\text{max}}=854\,\pc$. The orbit is plotted in \Gus{Appendix x}. We then
suppose that an observer makes observations of this orbit in a coordinate
system that is incorrect in radius by $200\,\pc$ and height by $100\,\pc$ ---
we subtract the vector $(200, 0, 100)\,\pc$ from each position in the orbit.
This corresponds to an observer physically located at the position $(8, 0,
0)\,\kpc$ but erroneously thinking they are located at $(8.2, 0, 0.1)\,\kpc$.

>>>>

First, we illustrate the time-dependence of one possible inaccurate reference
frame. We begin by taking an orbit with initial position $(8, 0, 0)\,\kpc$ and
initial velocity $(0, -190, 30)\,\kms$ --- this corresponds to an orbit with
actions $(J_r, L_z, J_z) = (37.9, -1520, 7.0)\,\actunit$ and
$z_{\text{max}}=425\,\pc$. The orbit is plotted in \Gus{Appendix x}. We then
suppose that an observer makes observations of this orbit in a coordinate
system that is incorrect in radius by $200\,\pc$ and height by $100\,\pc$ ---
we subtract the vector $(200, 0, 100)\,\pc$ from each position in the orbit.
This corresponds to an observer physically located at the position $(8, 0,
0)\,\kpc$ but erroneously thinking they are located at $(8.2, 0, 0.1)\,\kpc$.
